Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-07-23 manuscript/climate_sensitivity_SI.Rmd
Updated figure and table captions / fixed colnames #117

bark <- read.csv("tables_figures/publication/tableS2_bark_regression.csv", stringsAsFactors = FALSE)
bark[,2] <- NULL
colnames(bark) <- c("Species", "Equations", "$R^2$")
kable(bark, booktabs=TRUE, format = "latex", caption = "Table S2. Species-specific bark thickness regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

@@

heights <- read.csv("tables_figures/publication/tableS3_height_regression.csv", stringsAsFactors = FALSE)
kable(heights, booktabs=TRUE, format = 'latex', caption = "Table S3. Species-specific height regression equations", escape = FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position", protect_latex = TRUE)
```

\clearpage
```{r table S4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS4_singlevariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_all.csv`.
kable(singlevar_table, booktabs = TRUE, caption = "Table S4. Individual tests of species traits as drivers of drought resistance, where $Rt$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

@@

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS5_singlevariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(singlevar_table, booktabs = TRUE, caption = "Table S5. Individual tests of species traits as drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

@@

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.019, 1999: -0.005; same values in all top models).

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS7_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.03, 1999: 0.008; same values in all top models).

@@

\newpage
![**Figure S2. Map of ForestGEO plot showing topographic wetness index and location of cored trees**](tables_figures/publication/figureS2_location_cored_trees.png){width=500px}

@@

![**Figure S6. Visualization of best model, with data, for all droughts combined.** Model coefficients are given in Table S6.](tables_figures/publication/FigureS6_best_model_with_data.png)

>>>>

bark <- read.csv("tables_figures/publication/tableS2_bark_regression.csv", stringsAsFactors = FALSE)
bark[,2] <- NULL
colnames(bark) <- c("Species", "Equations", "$R^2$")
kable(bark, booktabs=TRUE, format = "latex", escape=FALSE, caption = "Table S2. Species-specific bark thickness regression equations") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

@@

heights <- read.csv("tables_figures/publication/tableS3_height_regression.csv", stringsAsFactors = FALSE)
colnames(heights)[3] <- "$R^2$"
kable(heights, booktabs=TRUE, format = 'latex', caption = "Table S3. Species-specific height regression equations", escape = FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position", protect_latex = TRUE)
```

\clearpage
```{r table S4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS4_singlevariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_all.csv`.
colnames(singlevar_table)[1] <- "variable"
kable(singlevar_table, booktabs = TRUE, caption = "Table S4. Individual tests of species traits as drivers of drought resistance, where $Rt$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

@@

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS5_singlevariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
colnames(singlevar_table)[1] <- "variable"
kable(singlevar_table, booktabs = TRUE, caption = "Table S5. Individual tests of species traits as drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

@@

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
colnames(multivar_table)[1] <- "drought"
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.019, 1999: -0.005; same values in all top models).

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS7_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
colnames(multivar_table)[1] <- "drought"
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.03, 1999: 0.008; same values in all top models).

@@

\newpage
![**Figure S2. Map of ForestGEO plot showing topographic wetness index and location of cored trees.** Scale units are in meters](tables_figures/publication/figureS2_location_cored_trees.png){width=500px}

@@

![**Figure S6. Visualization of the best model ($\Delta$AICc=0) with data for all droughts combined.** Model coefficients are given in Table S6.](tables_figures/publication/FigureS6_best_model_with_data.png)
